On Secure Delegation of SampBQP with a Classical Client

### 2020-03-15 bqp-rewrite.tex
Write down feedbacks from meeting

\nc{\ctx}[2]{\ensuremath{{{#1}^{(#2)}}}}

In this section we show a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
We start with the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
Generally one can obtain blindness by running a protocol under homomorphic encryption. \Ethan{Maybe cite?} In our case, we have a classical client and a quantum server, so we choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.

We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.
First, when the plaintext is classical, the encryption can be performed classically.
Moreover, a quantum ciphertext can be measured homomorphically, in which case the measurement outcomes can then be decrypted classically.
Lastly, the encryption is done qubit-by-qubit, so one can split a ciphertext into registers as one would with the corresponding plaintext.

We now state our compiler that gives any $\QPIP_0$ protocol blindness.
For notation, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{i}$ to denote $x$ encrypted under $pk_i$.
Otherwise, we write $x'$ for a ciphertext corresponding to plaintext $x$.
Moreover, the encryption is qubit-by-qubit,
so we can write $(x_1, x_2)'=(x_1', x_2')$.

@@

\begin{theorem}
	For all cheating prover $\Pblindstar$, there exists a cheating prover $\Pstar$ s.t. for all input $x$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
\end{theorem}
\begin{proof}
	We define $\Pstar$ so that on $\cPstar{1}$ it generates
	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
	$\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
	It then runs $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$.
	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p_1}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st_{P, 1}}{1}$ and $sk_1$.
	Then, on the rest of the $\cPstar{t}$ rounds, $\Pstar$ generates
	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$, and produces ciphertexts
	$\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
	It then runs $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$.
	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p_t}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st_{P, t}}{t}$ and $sk_t$.

>>>>

In this section we show a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
\Ethan{Talk about the compiler first, and BQP after.}
We start with the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
Generally one can obtain blindness by running a protocol under homomorphic encryption. \Ethan{Maybe cite?} In our case, we have a classical client and a quantum server, so we choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
\Ethan{Talk about FBQP too}

\nc{\ctx}[2]{\ensuremath{{{\widehat{#1}}^{(#2)}}}}

\Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}

\Ethan{Too bottom-up. Need to tell more story.}
We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.
First, when the plaintext is classical, the encryption can be performed classically.
Moreover, a quantum ciphertext can be measured homomorphically, in which case the measurement outcomes can then be decrypted classically.
Lastly, the encryption is done qubit-by-qubit, so one can split a ciphertext into registers as one would with the corresponding plaintext.

\Ethan{More story here. Talk about stuff like why switch keys.}

We now state our compiler that gives any $\QPIP_0$ protocol blindness.
For notation, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{i}$ to denote $x$ encrypted under $pk_i$.

@@

\begin{theorem}
	For all cheating prover $\Pblindstar$, there exists a cheating prover $\Pstar$ s.t. for all input $x$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
\end{theorem}
\begin{proof}
	We define $\Pstar$ so that \Ethan{Fix wording here} on $\cPstar{1}$ it generates
	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
	$\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
	It then runs $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$.
	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p_1}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st_{P, 1}}{1}$ and $sk_1$.

	Then, on the rest of the $\cPstar{t}$ rounds, $\Pstar$ generates
	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$, and produces ciphertexts
	$\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
	It then runs $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$.
	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p_t}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st_{P, t}}{t}$ and $sk_t$.
